Practical seed-recovery for the PCG Pseudo-Random Number Generator

### 2020-11-01 article/main.tex
Corrections article

\usepackage[utf8]{inputenc}
\usepackage{amssymb, amsmath, amsfonts, amscd}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{url}
\usepackage{xspace}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{tikz}
\usepackage{minted}
\usepackage{epigraph}
\usepackage{cellspace}
\usepackage{multirow}
\usetikzlibrary{patterns}
\usepackage[noend]{algpseudocode}

@@

\institute{% ordre alphabétique
Univ. Lille, CNRS, Centrale Lille, UMR 9189 - CRIStAL - Centre de Recherche en Informatique Signal et Automatique de Lille, F-59000 Lille, France \\ 
\email{charles.bouillaguet@univ-lille.fr}
\and 
Sorbonne Université, CNRS, LIP6, F-75005 Paris, France \\
\email{florette.martinez@lip6.fr}
\and 
Sorbonne Université, F-75005 Paris, France \\
\email{julia.sauvage@etu.upmc.fr}
}

@@

\begin{figure}
  \begin{minipage}[t]{5cm}
\begin{minted}[fontsize=\small,frame=single]{C}
u128 a;
u64 m = 0xda942042e4dd58b5;

u64_t lehmer64() 
{
    a *= m;
    return a >> 64;
}
\end{minted}
  \end{minipage}
    \begin{minipage}[t]{4cm}
% 128-bit LFSR
\begin{minted}[fontsize=\small,frame=single]{C}
u32 a, b, c, d;

@@

Therefore the algorithm requires $2^{41.67}$ CPU cycles in total; this makes
less than 5 cycles per iteration of the inner loop. We used several
implementation tricks to reach this level of efficiency:

@@

With $\ell=11$, the whole process took $2^{56.74}$ CPU cycles, which makes less
than 6 cycles per iteration of the inner loop. We used essentially the same
implementation tricks discussed above. However, this time we had to additionally
implement the \textsc{ConsistencyCheck} procedure, which is called in the inner
loop. We observed that the set of possible candidate values $\mathcal{C}$ only
depends on $w_0$ (the variable of the outer loop). Therefore, before entering
the inner loop, we precompute a bit field of size $2^\ell$ describing
$\mathcal{C}_i$. To simplify the implementation, we flatten them by computing
$\mathcal{C} = \cup_i \mathcal{C}_i$. This slightly increase the probability of
false positives, but makes our code slightly simpler.

@@

% pas dans la version anonyme.
\paragraph{Acknowledgements.} The authors thank Thomas Espitau, Damien Vergnaud
and Vincent Zucca for helpful discussions. We also thank Léo Ducas for helping
us with the \texttt{G6K} library and Melissa O'Neil for kindly indulging our
request for challenge inputs.

>>>>

\usepackage[utf8]{inputenc}
\usepackage{amssymb, amsmath, amsfonts, amscd}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage[hyphens]{url}
\usepackage{xspace}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{tikz}
\usepackage{minted}
\usepackage{epigraph}
\usepackage{cellspace}
\usepackage{multirow}
\usetikzlibrary{patterns}
\usepackage[noend]{algpseudocode}

@@

\institute{% ordre alphabétique
Univ. Lille, CNRS, Centrale Lille, UMR 9189 - CRIStAL - Centre de Recherche en Informatique Signal et Automatique de Lille, F-59000 Lille, France \\ 
\email{charles.bouillaguet@univ-lille.fr}
\and 
Sorbonne Université, CNRS, LIP6, F-75005 Paris, France \\
\email{florette.martinez@lip6.fr}
\and 
Sorbonne Université, F-75005 Paris, France \\
\email{julia.sauvage@etu.sorbonne-universite.fr}
}

@@

\begin{figure}
  \begin{minipage}[t]{5cm}
\begin{minted}[fontsize=\small,frame=single]{C}
u128 a;

u64_t lehmer64() 
{
    a *= 0xda942042e4dd58b5;
    return a >> 64;
}
\end{minted}
  \end{minipage}
    \begin{minipage}[t]{4cm}
% 128-bit LFSR
\begin{minted}[fontsize=\small,frame=single]{C}
u32 a, b, c, d;

@@

Therefore the algorithm requires $2^{41.67}$ CPU cycles in total; this makes
less than 26 cycles per iteration of the inner loop. We used several
implementation tricks to reach this level of efficiency:

@@

With $\ell=11$, the whole process took $2^{56.74}$ CPU cycles, which makes less
than 54 cycles per iteration of the inner loop. We used essentially the same
implementation tricks discussed above. However, this time we had to additionally
implement the \textsc{ConsistencyCheck} procedure, which is called in the inner
loop. We observed that the set of possible candidate values $\mathcal{C}$ only
depends on $w_0$ (the variable of the outer loop). Therefore, before entering
the inner loop, we precompute a bit field of size $2^\ell$ describing
$\mathcal{C}_i$. To simplify the implementation, we flatten them by computing
$\mathcal{C} = \cup_i \mathcal{C}_i$. This slightly increase the probability of
false positives, but makes our code slightly simpler.

@@

% pas dans la version anonyme.
\paragraph{Acknowledgements.} The authors thank Thomas Espitau, Virgile Tellier,
Damien Vergnaud and Vincent Zucca for helpful discussions. We also thank Léo
Ducas for helping us with the \texttt{G6K} library and Melissa O'Neil for kindly
indulging our request for challenge inputs. We finally thank Alexandra Assanovna
Elbakyan for helping scientists to access the works of their colleagues.
